SoK: Application Attack Defenses (in Question)

### 2014-10-07 docs/questioning.tex
more on methodology

>>>>

In what follows we evaluate published research in attack detection
mechanism based on the following:
\begin{itemize}
\item Reporting of values for True Positives ($a$), False Positives
  ($b$), False Negatives ($c$), True Negatives ($d$), on test
  environments.
\item Reporting of values for True Positives ($A$), False Positives
  ($B$), False Negatives ($C$), True Negatives ($D$), on the
  performance of the mechanism on environment with real attack
  profiles.
\end{itemize}
